---
title: "Data Analysis for PSA Results"
author: "Alex & Rusheel"
date: "29/03/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Answers to Questions

**Determine the incremental cost-effectiveness ratio (ICER) of the intervention strategy compared
with the control stategy.**

``` {r "Part_2/PSA-Analysis.R", echo=FALSE}
load("Part_2/PSA-environment.RData")
print(ICER)
```

As we can see, the ICER is about €28,000. This would be acceptable if society were willing to pay €80,000 per QALY but not if society were willing to pay only €20,000 per QALY.

**Create an incremental cost-effectiveness plane and visualize the incremental effects (x-axis) and
incremental costs (y-axis) of the intervention strategy compared with the control strategy.
Provide a correct label for both axes.**

```{r}
plot(plane, xlab="Incremental effects", ylab="Incremental costs")
```
**Add two solid lines to this plane, one representing a willingness-to-pay (WTP) threshold of
€20,000 per QALY gained, and one representing a willingness-to-pay threshold of €80,000 per
QALY gained.**

```{r}
WTP_plot
```
**Determine how many of the PSA samples fall below these respective WTP thresholds.**

```{r}
percentage_below_20000
percentage_below_80000
```
**Finally, vary the WTP from €0 to €200,000 per QALY, in steps of €1,000, and determine for each
WTP value the fraction of samples (points) falling below that specific WTP. This fraction
represents the probability that the intervention strategy has acceptable cost-effectiveness
compared with the control strategy, given that specific WTP. Create a cost-effectiveness
acceptability curve (CEAC) that visualizes this probability as a function of the WTP over this
range. Also, provide correct labels for both axes.**

```{r}
plot(x=seq(0, 200000, length.out = 201), y=percentages_vector, xlab="Willingness to Pay Threshold",
  ylab="Points below WTP curve", main="CEAC curve")
```

**What is your conclusion based on this CEAC?**

About 60% of the points (representing a simulation run) will fall below a WTP threshold of €50,000. Beyond that the curve flattens off. For a more plausible WTP of €20,000 (used in the Netherlands) only 40% of the values will be below it. In conclusion, this intervention strategy is not cost effective at any reasonable WTP.

